### 2022-11-15 paper/icse23/RESPONSE.txt

Thank you for the comments.

__REVIEW_1

>Differences with prior grammar-based work (e.g., MT-NLP, Astraea,
 Ogma etc)

Our method is a grammar-based behavioral testing method for over
linguistic capabilities(LCs) while the existing work (Ogma, Astraea and
MT-NLP) focus on testing fairness and erroneous inputs.  Second, our
method keeps label consistency while prior work doesn't garauntee the
label consistency as they only focus on input generation. Third, ours
generates input with new structure while others relies on the
original structure and replaces words based on their manually
generated grammar. Additionally, the existing work randomly selects
words, but our work selects grammatically and contextually natural
words suggested from CFG grammar and word suggestion model.

>Introducing the linguistic capability...the loop framework.

Our work uses the same linguistic capabilities introduced in
CEHCKLIST.

>Effort involved in specifying the rules?

LCs in CHECKLIST are ambiguously described in a sentence. Thus, we
manually extract elements of interests for each LCs in CHECKLIST. In
practice, we spent less than 10 min to generate each LC.

__REVIEW_2

### 2022-11-15 paper/icse23/RESPONSE.txt

>Effort involved in specifying the rules?

LCs in CHECKLIST are ambiguously described in a sentence. Thus, we
manually extract elements of interests for each LCs in CHECKLIST. In
practice, we spent less than 10 min to generate each LC.

__REVIEW_2

>Do not see a clear motivation of using linguistic capabilities.

Our work uses the same LCs provided in CEHCKLIST. They describes
specific metamorphic relations between linguistic patten in input and
output. It enables behavior testing and finding erroneous patterns of
models.

>Generalizability of the proposed method seems limited.

>Comparison of S^2LCT with NLP adversarial machine learning.

S^2LCT evaluate model behavior under task-relevant LCs. It generates
test cases suitable to evalaute model given LC rather error-causing
test cases.

>No discussion or results about repair strategy.

Section VI

__REVIEW_3

### 2022-11-16 paper/icse23/RESPONSE.txt

Thank you for the comments.

__REVIEW_1

>Differences with prior grammar-based work (e.g., MT-NLP, Astraea,
 Ogma etc)

Our method is a grammar-based behavioral testing method for over
linguistic capabilities(LCs). On the other hand, to best of my
knowledge, the existing work (e.g. Ogma, Astraea and MT-NLP) focus on
testing fairness or generating adversarial inputs.  Second, our method
secure label consistency by only allowing neutral words from the set
of contextually suggested words while prior work does not garauntee
the label consistency as they only focus on input generation. For
example, Ogma and Astraea replace a word with a different word that
has same part-of-speech. the method is limited to secure the semantic
of input sentence, and it does not gaurantee same label as a
result. Third, ours generates new test cases with a variety of new
input structures while others rely on the original structure, new
input sentences are limited to the original structure based on their
manually generated grammar. Additionally, our work selects
grammatically and contextually natural words suggested from CFG
grammar and word suggestion model. In contrast, the existing work
randomly selects words.

>How much effort involved in specifying the rules?

LCs in CHECKLIST are described in a sentence, thus it is not clear to
specify linguistic characteristics of interest and how the input and
output should be formed because of semantic and structure diversity in
natural language. Thus, we manually specify rule for seed generation
for each LCs in CHECKLIST to achieve the semantic and structure
diversity. In practice, we spent less than 10 min to generate each LC.

@@

>Introducing the linguistic capability...the loop framework.

Our work uses the same LCs provided in CHECKLIST. The LCs are
pre-defined manually for each task of interest.

@@

__REVIEW_2

>Do not see a clear motivation of using linguistic capabilities.

Our work uses the same LCs provided in CEHCKLIST. They describe
specific metamorphic relations between linguistic patten in input
sentence and its output. Compared to the traditional train-valid-test
split to test NLP models aggregately, Use of the LCs is able to assess
NLP models over multiple linguistic characteristics in natural
language relevant to task. Therefore, it enables model behavior
testing finding erroneous patterns of models.

>Comparison of S^2LCT with NLP adversarial machine learning [2-5].

Extended from the previous response above, S^2LCT evaluates model
behavior under task-relevant LCs. S^2LCT generates test cases suitable
to given LC. Compared with out work, adversarial approaches focus on
generating error-causing test cases. It is limited to assess NLP
models over multiple linguistic characteristics.

>Generalizability of the proposed method seems limited.

S^2LCT is also implemented for hate speech detection task.  We will
add results of the task in our final version [JL] or appendix?.

>No discussion or results about repair strategy.

In the section VI of our paper, we show the effectiveness of S^2LCT
for finding root causes of bugs.

__REVIEW_3

>Limited Applicability & Generalizability

See response to REVIEW_2

>Fail Rate for CHECKLIST

[JL] do we add the numbers here or say that we will add that in the
appendix? or final version?

>Production rule coverage.: We
[JL] Do we answer the question?

>label consistency results for CHECKLIST

[JL] do we add the numbers here or say that we will add that in the appendix?

### 2022-11-17 paper/icse23/RESPONSE.txt

uniqueness of the test generation over lc
difference metamorphic testing than our work

ours: both label-consistency and LC-consistency
manually discovered label consistency

1. we generate new structure than other work

our work more generally preserves semantic context(capability part)
and grammatical correctness(syntactical part).

==========
Thank you for the comments.

__REVIEW_1&2

>Uniqueness of S^2LCT over prior work (MT-NLP, Astraea, Ogma and
 adversarial methods for NLP models)

S^2LCT is based on a grammar based test case generation method. The
uniqueness of the S^2LCT stems from the following properties: First,
S^2LCT generates new test cases with new and diverse input structures
given the grammar obtained from commonly used large corpus.  Compared
with the method, Astraea and Ogma generates input sentences by
replacing words in an original sentences with other wrods with same
tag of part-of-speech (POS) conforming to the grammar manually
constructed. In addition, MT-NLP both replaces words and expands input
structure, but the expansion only relies on a addition of adjective
word before noun. In our paper, the structural diversity is shown by
production rule coverage. Second, S^2LCT addresses consistency of
label and linguistic capability (LC). The Ogma does not aim to
preserve the semantic similarity, and it causes label inconsistency in
input generation. In addition, Astraea and MT-NLP manually preserves
label consistency by only relying on limited grammar attributes
(e.g. replacement of noun words). Compared with it, S^2LCT preserves
label and LC consistency by analyzing syntactic and semantic
appropriateness of expanded words in the input sentence. Besides,
S^2LCT generates test cases suitable to the LC and assess how the
model behaves on a specific linguistic characteristics in input
sentences. This method is different from the adversarial methods in a
sense that the adversarial approaches rely on generating error-causing
test cases, and they are limited to assess NLP models on multiple
linguistic characteristics.

>Motivation of using linguistic capabilities

Traditional train-valid-test split tests NLP models aggregately and
the test set reveals biases and fail to comprehensive testing the
models. Therefore, prior work (e.g. CHECKLIST) introduced multiple
task relevant LCs and relevant test cases. It enables assess NLP
models over the multiple LCs. However, it requires manual effort to
generate relevant test cases, and it results in obtaining limited
semantic and syntactic attributes. In addition, It requires
non-trivial manual efforts to define the metamorphic relations between
inputs and outputs beacuse semantics of nature language can be greatly
changed even by a slight perturbation to the sentences. In this work,
we automates LC-relevant test cases generation using the same LCs
provided in CEHCKLIST.

__REVIEW_2&3

>Limited Applicability & Generalizability

S^2LCT is also implemented for hate speech detection task.
# TODO: add HS results
We will also add the results of the task in our final version.

@@

__REVIEW_1

>How much effort involved in specifying the rules?

LCs in CHECKLIST are described in a sentence, thus it is not clear to
specify linguistic characteristics of interest and how the input and
output should be formed because of semantic and structure diversity in
natural language. Thus, we manually specify rule for seed generation
for each LCs in CHECKLIST to achieve the semantic and structure
diversity. In practice, we spent less than 10 min to generate each LC.

@@

__REVIEW_2

>No discussion or results about repair strategy.

In the section VI of our paper, we show the effectiveness of S^2LCT
for finding root causes of bugs.

__REVIEW_3

>Significant effort in defining search rules and transformation

I agree that S^2LCT requires manual specification of search rules and
transformation.

>Fail Rate for CHECKLIST
# TODO: add numbers here

>Label Consistency

During the manual study to measure label consistency, it is observered
that the 83% of label consistency of the seed sentences comes from
inconsistency between label and the raw sentences in the dataset, and
it results in the 84% of label consistency of expanded
sentences. Accordingly, we also empirically compare seed sentences and
their expanded sentences from the pass-to-fail cases in the table II
to check the label consistency of the expanded sentences. From the
comparison, it is observed that no expanded words change the sentiment
of the expanded sentences and the expanded words preserves the label
consistency.
# TODO: Check the label consistency on the example of pass-to-fail manually.

### 2022-11-17 paper/icse23/RESPONSE.txt

__REVIEW_3

>Significant effort in defining search rules and transformation

I agree that S^2LCT requires manual specification of search rules and
transformation.

>Fail Rate for CHECKLIST

LC1(Short sentences with neutral adjectives and nouns): BERT:77.51%, RoBERTa:81.06%, DistilBERT:96.79%
LC2(Short sentences with sentiment-laden adjectives): BERT:0.3%, RoBERTa:1.61%, DistilBERT:1.44%
LC3(Sentiment change over time, present should prevail): BERT:21%, RoBERTa:10.36% DistilBERT:31.65%
LC4(Negated negative should be positive or neutral): BERT:11.77%, RoBERTa:3.21%, DistilBERT:10.82%
LC5(Negated neutral should still be neutral): BERT:97.24%, RoBERTa:92.31%, DistilBERT:98.16%
LC6(Negation of negative at the end, should be positive or neutral): BERT:88.09%, RoBERTa:20.95%, DistilBERT:100%
LC7(Negated positive with neutral content in the middle): BERT:86%, RoBERTa:41.6%, DistilBERT:86.5%
LC8(Author sentiment is more important than of others): BERT:43.87%, RoBERTa:31.57%, DistilBERT:41.45%
LC9(Parsing sentiment in (question, yes) form): BERT:19.48%, RoBERTa:13.71%, DistilBERT:16.92%
LC10(Parsing sentiment in (question, no) form): BERT:53.06%, RoBERTa:59.86%, DistilBERT:84.25%

### 2022-11-18 paper/icse23/tables/test-results-hs-all-numbers.tex
new table

@@

@@

>>>>

\DefMacro{test-results-hs-lc10}{Hate expressed through reference in subsequent clauses}
\DefMacro{test-results-hs-lc10-num-seeds}{11968}
\DefMacro{test-results-hs-lc10-num-exps}{44890}
\DefMacro{test-results-hs-model0-lc10-num-all-fail}{5,984}
\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{10.52}
\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc11}{Hate expressed through reference in subsequent sentences}
\DefMacro{test-results-hs-lc11-num-seeds}{11968}
\DefMacro{test-results-hs-lc11-num-exps}{42840}
\DefMacro{test-results-hs-model0-lc11-num-all-fail}{5,984}
\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{10.92}
\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc12}{Hate expressed using negated positive statement}
\DefMacro{test-results-hs-lc12-num-seeds}{23379}
\DefMacro{test-results-hs-lc12-num-exps}{126742}
\DefMacro{test-results-hs-model0-lc12-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{0}

@@

\DefMacro{test-results-hs-model1-lc10-num-all-fail}{48,776}
\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{49.97}
\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{95.33}
\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{85.79}
\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{1,164}
\DefMacro{test-results-hs-model1-lc11-num-all-fail}{46,721}
\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{49.72}
\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{95.17}
\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{85.24}
\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{1,070}
\DefMacro{test-results-hs-model1-lc12-num-all-fail}{144,823}
\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{96.71}
\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{96.47}
\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{2,804}

@@

\DefMacro{test-results-hs-model2-lc10-num-all-fail}{48,642}
\DefMacro{test-results-hs-model2-lc10-num-seed-failrate}{49.85}
\DefMacro{test-results-hs-model2-lc10-num-exp-failrate}{95.07}
\DefMacro{test-results-hs-model2-lc10-num-all-failrate}{85.55}
\DefMacro{test-results-hs-model2-lc10-num-pass-to-fail}{1,169}
\DefMacro{test-results-hs-model2-lc11-num-all-fail}{46,156}
\DefMacro{test-results-hs-model2-lc11-num-seed-failrate}{49.41}
\DefMacro{test-results-hs-model2-lc11-num-exp-failrate}{93.94}
\DefMacro{test-results-hs-model2-lc11-num-all-failrate}{84.21}
\DefMacro{test-results-hs-model2-lc11-num-pass-to-fail}{1,726}
\DefMacro{test-results-hs-model2-lc12-num-all-fail}{145,761}
\DefMacro{test-results-hs-model2-lc12-num-seed-failrate}{97.03}
\DefMacro{test-results-hs-model2-lc12-num-exp-failrate}{97.11}
\DefMacro{test-results-hs-model2-lc12-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model2-lc12-num-pass-to-fail}{2,290}

### 2022-11-18 paper/icse23/tables/test-results-hs-table.tex
new table

>>>>

\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc10-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-pass-to-fail}\\
\multirow{3}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc11-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-pass-to-fail}\\
\multirow{3}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc12-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-pass-to-fail}\\
